Verifying Demonstrations

### 2017-09-28 protocol.tex

>>>>

\subsubsection{Architecture}

We also have an architectural problem.
If the system is only run by volunteering activists, then Eve can simply 
analyse network traffic and look for people running nodes in the system.

\begin{question}
  Shall we offer a platform that is run by a variety of institutions who 
  offers to verify protests?
  Or go strictly peer-to-peer?
\end{question}

\begin{question}
  If strictly peer-to-peer, and only run by protesters, one can infer that 
  they are protesters by running such a node.
  Can this be mitigated?
\end{question}

Similarly, we have the problem of how protesters submit their proofs to the 
system.
This must be done anonymously.
Otherwise Eve can analyse the network traffic to find out who submitted proofs 
to the system.
The main problem here is that the participants must be indistinguishable from 
non-participants.
This means that we cannot use special-purpose anonymizing 
technologies.

\begin{question}
  How do we submit the proofs to storage?
  Voting normally uses mix-nets (provable shuffles).
\end{question}

\begin{remark}
  We must mix participants with non-participants.
\end{remark}

### 2017-09-28 security.tex
Changes section title of security analysis

\section{Security}

>>>>

\section{Security and privacy analysis}%
\label{SecurityAnalysis}

\subsection{Assumptions}

We assume that every participant has a device similar to a smartphone.
Throughout this text, when we refer to a participant, say Alice, we actually 
mean a principal which can perform cryptographic operations and communicate with 
other local devices on Alice's behalf.
(This means that we essentially provide a lower bound for the participation 
count, since some participants might not have such a device.)

\mode<presentation>{%
\begin{frame}
  \begin{center}
    Alice $:=$ Alice's cryptographic device
  \end{center}
\end{frame}
}

No connection to any global network the Internet is necessary during the 
protest.
During the protest these devices are computationally limited by their 
batteries.
Before and after the protest, we assume that the devices have Internet 
connections and are not computationally limited by any battery.

\mode<presentation>{%
\begin{frame}
  \begin{assumption}[During protest]
    \begin{itemize}
      \item Everyone has a smartphone.
      \item Can use ad-hoc networks during the event.
      \item Computations bounded by battery life.
    \end{itemize}
  \end{assumption}

  \pause{}

  \begin{assumption}[Before and after protest]
    \begin{itemize}
      \item Internet connection available.
      \item Computations not bounded by battery life.
    \end{itemize}
  \end{assumption}

  \pause{}

  \begin{remark}
    We provide a lower bound, since there might be participants without phones.
  \end{remark}
\end{frame}
}

We further assume that every participant has a digital certificate signed by 
some logically centralized certificate authority.
E.g.\ that we can use the cryptographic keys stored in the chip of the national 
identity card or passport.
We need this to prevent Sybil attacks~\cite{SybilAttack}.
